non_phylo_analyses

### 2018-04-11 reports/non_phylo_model.Rmd
some modelling work

checking for multicolinearity
```{r}
library(car)
vif()
```

@@

>>>>

checking for multicolinearity
```{r}
library(car)
vif(naive_mod)
```

@@

```{r}
df3 <- df2 %>%
  mutate(response = log(urban_median)) %>%
  mutate(body_size_logged = log(mean_body_size)) %>%
  mutate(clutch_size_logged = log(clutch_size))
```

a model averaging approach
small model first

```{r}
glob.mod <- lm(response~body_size_logged+clutch_size_logged+feeding_habitat_generalism+brain_residual+Habitat_agricultural,data=df3,na.action="na.fail",weights=(df3$N/df3$unique_localities))

library(arm)

stdz.model <- standardize(glob.mod)
model.set <- dredge(stdz.model)

model.set

#### selects all models with deltaAic < 4
top.models <- get.models(model.set, cumsum(weight) <= 0.95)

#### how many top models
length(top.models)

#### Ranks these models based on AICc
my.models <- model.sel(top.models, rank="AICc")

 #### Prints the top models (selected above)
print.data.frame(my.models, digits=2)

Averaged_models <- model.avg(top.models)

summary(Averaged_models)
confint(Averaged_models, full=TRUE)
```

run a parallel version
```{r}
library(snow)
clusterType <- if(length(find.package("snow", quiet = TRUE))) "SOCK" else "PSOCK"
clust <- try(makeCluster(getOption("cl.cores", 10), type = clusterType))

clusterExport(clust, "df3")

glob.mod <- lm(response~body_size_logged+clutch_size_logged+feeding_habitat_generalism+brain_residual+Habitat_agricultural,data=df3,na.action="na.fail",weights=(df3$N/df3$unique_localities))

library(arm)

stdz.model <- standardize(glob.mod)

model.set <- pdredge(stdz.model, cluster=clust)

model.set

#### selects all models with deltaAic < 4
top.models <- get.models(model.set, cumsum(weight) <= 0.95)

#### how many top models
length(top.models)

#### Ranks these models based on AICc
my.models <- model.sel(top.models, rank="AICc")

#### Prints the top models (selected above)
print.data.frame(my.models, digits=2)

Averaged_models <- model.avg(top.models)

summary(Averaged_models)
confint(Averaged_models, full=TRUE)

Now repeat on the full model (will take a while so let it run overnight)
```{r}
library(snow)
clusterType <- if(length(find.package("snow", quiet = TRUE))) "SOCK" else "PSOCK"
clust <- try(makeCluster(getOption("cl.cores", 10), type = clusterType))

clusterExport(clust, "df3")

glob.mod <- lm(response ~ body_size_logged + clutch_size_logged + feeding_habitat_generalism + brain_residual + Habitat_agricultural +
                 breeding_habitat_generalism + granivore + insectivore + carrion_eater + plant_eater + diet_generalism + movement_class +
                 ground_nesting + hollow_nesting + nest_generalism + breeding + nest_aggregation + feeding_aggregation + Habitat_grass_shrubland +
                 Habitat_tree_forest, data=df3, na.action = "na.fail", weights=(df3$N/df3$unique_localities))

library(arm)

stdz.model <- standardize(glob.mod)

model.set <- pdredge(stdz.model, m.lim=c(0, 11), cluster=clust, extra="R^2")

model.set

#### selects all models with deltaAic < 4
top.models <- get.models(model.set, subset=delta<4)

#### how many top models
length(top.models)

#### Ranks these models based on AICc
my.models <- model.sel(top.models, rank="AICc")

 #### Prints the top models (selected above)
print.data.frame(my.models, digits=2)

Averaged_models <- model.avg(top.models)

summary(Averaged_models)
confint(Averaged_models, full=TRUE)
